preprocessing

### 2022-10-24 r-prep/prep.Rmd
2020

data_base = data_gwp100 %>%
  left_join(data_wdi,by=c("ISO","year")) %>%
  mutate(GHG_pc = GHG/pop) %>%
  mutate(GDP_pc = gdp_ppp/pop)

>>>>

data_base = data_gwp100 %>%
  left_join(data_wdi,by=c("ISO","year")) %>%
  mutate(GHG_pc = GHG/pop) %>%
  mutate(GDP_pc = gdp_ppp/pop) %>%
  filter(year <= 2019) %>% 
  mutate(EU= case_when(country %cin% eurostat::eu_countries[2]~ "Yes"))
